---
title: "Bibliometria4RA"
author: "HRico"
date: "22/3/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## upload libraries

```{r libraries, include=FALSE}
library(bibliometrix)
library(writexl)
library(wordcloud2)
library(stringr)
library(broom)
library(tidyverse)
library(gplots)
library(heatmaply)
library(readxl)
library(igraph)
library(tm)
```

# Get the DataSets

We get the data that was exported from WoS and Scopus. .bib extension is used from both data bases.

```{r cargaDB}

 file <- "Your Path/your_Scopus_filename.bib" 

file2 <- "Your Path/your_WoS_filename.bib"

```

## Merge Datasets

convert the data into data frames in order to merge both dataset in one.
We use Bibliometrix packages. We get w_sDF as a bibliometrix object

```{r merge}
scopusDF <- convert2df(file = file, dbsource = "scopus", format = "bibtex")
wosDF <- convert2df(file = file2, dbsource = "wos", format = "bibtex") 
w_sDF <- mergeDbSources(scopusDF,wosDF, remove.duplicated = TRUE)
```

Data frame columns are named using the standard Clarivate Analytics WoS
Field Tag codify.

The main field tags are:

| Field Tag | Description                                   |
|-----------|-----------------------------------------------|
| AU        | Authors                                       |
| TI        | Document Title                                |
| SO        | Publication Name (or Source)                  |
| JI        | ISO Source Abbreviation                       |
| DT        | Document Type                                 |
| DE        | Authors' Keywords                             |
| ID        | Keywords associated by SCOPUS or ISI database |
| AB        | Abstract                                      |
| C1        | Author Address                                |
| RP        | Reprint Address                               |
| CR        | Cited References                              |
| TC        | Times Cited                                   |
| PY        | Year                                          |
| SC        | Subject Category                              |
| UT        | Unique Article Identifier                     |
| DB        | Bibliographic Database                        |

## Cleaning

We review and clean de merged dataframe. Human review is taken place

-   Delete all raw whithout author in the field AU (field Tag = AU)
-   Delete duplicated raws:
 
  Publication year	/	Authors

2019	RHR A;BERGER B;HESS T
2020	ALTUNTAS Y;KOCAMAZ A;ULKGUN A
2021	SLAUGHTER K;CHEN D



```{r cleanning}
# check references without Authors
noAU_Rows<-which(w_sDF$AU=="NA N") 
w_sDF<-w_sDF[-c(noAU_Rows),]

 # find duplicated indexes
dupDocs<-which(w_sDF$AU=="RHR A;BERGER B;HESS T") 

# delete duplicated Reference
w_sDF<-w_sDF[-c(dupDocs),] 
```

# Homogenization

the objective is to homogenize the parts of the data frame that we obtain when performing a
merge from WoS and Scopus databases. In the *CR* Tag the
structure given to the part of the text that refers to the authors (AU) is different

*Scopus: AU= 'Surname', 'Initials'.,* WoS: AU= 'Surname''Initials'.,

This difference creates problems later on when using functions like
**localCitations** or **histNetwork** in which you use the *SR* tag to
perform those analyses. *SR* is a summary structure that it is used as pattern 
in search queries within *CR*. *SR* characterizes the author (AU) with
the WoS structure, so if we use a data frame merged between Scopus and WoS, 
the analysis we get is not complete.

The end of each reference is ";" in both cases.

```{r homogenizing}
library(stringr)

w_sDF$CR <- str_replace_all(w_sDF$CR,",((?=\\s[:alpha:].,)|(?=\\s[:alpha:].[:alpha:].,))","")

w_sDF_H <- w_sDF
```

## Exports the diferent data frames we built:


**dataframe to excel** with this format allows us to load the dataframe
in bilbioshiny() as a bibliometrix file and use all the analyses in that package. Very usefull to descriptive analysis.

```{r DF2Biblioshiny, include=FALSE}
# standardized
write_xlsx(w_sDF_H,"your Path/RA_results.xlsx")

# non standardized
write_xlsx(w_sDF,"your path/RA_results2.xlsx")
```


# ----- RELATIONAL ANALISYS -----------------

## Keyword analysis

the objective is to perform a descriptive analysis of the keywords that represent the Robo Advisor research, based on our collection of documents.In the data frame that we are using, they are found in the following fields:

-   TI: Document Titleo
-   DE: Author Keywords
-   ID: Keyword plus, Algorithm performed by bilbiometrix() to find the keywords in the titles of the cited references, besides in the refereces cited by the author.
-   AB: Abstracts

#### cleaning no relevant words

Any term-word that include "robo-advi*","robo*" and "Advi*" is included into the stopwords list.
We will use the function TermExtraction().

##### termExtraction() description

' Term extraction tool from textual fields of a manuscript

It extracts terms from a text field (abstract, title, author's keywords,
etc.) of a bibliographic data frame.

-   @param **M** is a data frame obtained by the converting function
    \code{\link{convert2df}}. It is a data matrix with cases
    corresponding to articles and variables to Field Tag in the original
    WoS or SCOPUS file.

-   @param **Field** is a character object. It indicates the field tag
    of textual data :

-   \\tabular{lll}{

-   \code{"TI"}\tab \\tab Manuscript title\cr

-   \code{"AB"}\tab \\tab Manuscript abstract\cr

-   \code{"ID"}\tab \\tab Manuscript keywords plus\cr

-   \code{"DE"}\tab \\tab Manuscript author's keywords}



## Building the  RA_STOPWORDS

### 1- extraction of keywords

we make a first extraction of the keywords from the tags TI,DE,AB to build with this list of words the stopwords and the thesaurus manually.

Step 1. Extraction of raw terms: Using the function termExtraction of the package bibliometrix, we extract from the AB and the DE a list of relevant keywords about RA, which we will call throughout this work as RA-K. Compound terms have been extracted from up to a maximum of 3 simple words (ngrams = 1 to 3). 

Step 2. Creation of RA-stopwords: When a bibliometric analysis based on keywords is carried out, having these stopwords in the preprocessing phase helps to obtain more focused results on the research topic, since all those words that they have no relevant meaning to the study. Considerating of this list allows greater visibility to be given to those terms that really add value and meaning to the subject being discussed. Thus, from the total of terms extracted in step 1, 1598 words or concepts have been obtained that were considered irrelevant for the analysis on RA  . Along with the stopwords that come by default in the bibliometrix package, all possible combinations of the terms Robo + Advi * have been included, since it is the initial query with which the database was obtained. The names of authors and countries have also been considered stopwords, since the analysis of both concepts has been carried out in the previous section.

```{r raw term extraction from DE , AB tags}

# Temp Data frame

myDF <- w_sDF_H

#load default stopwords
sw <- stopwords("english") 

RA_Keyword_DE <- termExtraction(myDF,Field="DE",remove.terms = sw)
DE_Terms <- sort(table(unlist(strsplit(RA_Keyword_DE$DE_TM,split=";"))),decreasing = TRUE)
DE_TermsDF <- as.data.frame(DE_Terms)

# delete  "NA" rows in field "DE"
DE_TermsDF <-  DE_TermsDF[DE_TermsDF$Var1!="NA",]

# export to csv
write.csv2(DE_TermsDF,file="your path/DE_Terms.csv")

# extract list of terms into the tag "AB" and differente ngrams. ngrams = 1 to 3
AB_Rawn1 <- termExtraction(myDF,Field="AB",ngrams = 1, remove.terms = sw)

AB_Rawn1 <- sort(table(unlist(strsplit(AB_Rawn1$AB_TM,split=";"))),decreasing = TRUE)

AB_Rawn1DF <- as.data.frame(AB_Rawn1)

AB_Rawn2 <- termExtraction(myDF,Field="AB",ngrams = 2, remove.terms = sw)

AB_Rawn2 <- sort(table(unlist(strsplit(AB_Rawn2$AB_TM,split=";"))),decreasing = TRUE)

AB_Rawn2DF <- as.data.frame(AB_Rawn2)

AB_Rawn3 <- termExtraction(myDF,Field="AB",ngrams = 3, remove.terms = sw)

AB_Rawn3 <- sort(table(unlist(strsplit(AB_Rawn3$AB_TM,split=";"))),decreasing = TRUE)

AB_Rawn3DF <- as.data.frame(AB_Rawn3)

#build a table with all of termse
Term_Raw <- rbind(DE_TermsDF,AB_Rawn1DF,AB_Rawn2DF,AB_Rawn3DF) 

Term_Raw2<- rbind(DE_TermsDF,AB_Rawn1DF,AB_Rawn2DF) 

#export to csv to manually build the RA Stopwords

write.csv2(Term_Raw,file="your path/Raw_Terms.csv")

```


## Remove words

. Building the final stopword list. RA_Stopwords.xlsx is the RA_Stopwords list built manually.

```{r remove words, include=FALSE}

sw <- stopwords("english") 
RA_Stopwords <- read_excel("your path/RA_Stopwords.xlsx",  sheet = "Stopwords")

RA_Stopwords <- c(RA_Stopwords$StopWords) # char vector
# lowe case
RA_Stopwords <- tolower(RA_Stopwords)

# merge both stopwrds list

remove.terms <- c(RA_Stopwords,sw)

# uppercase
remove.terms <- toupper(remove.terms)

```


DE --run termExtraction()

we do a special analysis of the author keywords, repeating the term extraction but with the full removed word list

```{r run analysis DE}
myDF <- w_sDF_H



RA_Keyword_DE <- termExtraction(myDF,Field="DE",remove.terms = remove.terms)
DE_Terms <- sort(table(unlist(strsplit(RA_Keyword_DE$DE_TM,split=";"))),decreasing = TRUE)
DE_TermsDF <- as.data.frame(DE_Terms)

# Delete "NA" rows
DE_TermsDF <-  DE_TermsDF[DE_TermsDF$Var1!="NA",]

# export to csv. we will check it manually
write.csv2(DE_TermsDF,file="your path/DE_Terms.csv")

```


## building thesaurus


we prepare all the dictionaries of synonyms, this allows us to group the output of the function into conceptual blocks.

- Step 3. Creation of RA-synonyms. This dictionary will facilitate the analysis of the relevance of the different topics covered in the RA research, by allowing all those words that refer to the same topic or concept to be grouped into families. Thus, after obtaining the list of RA-stopwords, all the terms of interest on RA have been extracted from the DE and AB, obtaining a total of 4018 words. Of these, the 471 RA-K have been selected, which are considered to represent all those topics of interest for the analysis of the RA (see Table A2 in the appendix). The RA-K has been grouped into 20 families or conceptual groups that, additionally, have been identified with the different phases of the IAds process, which will allow us to study the relevance of each of these phases in the research collected in the corpus.


the first word of each string row is taken as the main word and the rest of the row are its synonyms.

#Load de synonyms, RA_sinonimos.xlsx


```{r Load synonyms, include=FALSE}
library(readxl)

RA_Sinonimos <- read_excel("your path/RA_sinonimos.xlsx",  sheet = "KeyWd_synonyms")


```

## transform into a char vector. we will need later


```{r Synonyms}


nCampos <- ncol(RA_Sinonimos) # number of fields


#char vector
synonyms_RA <- character()

for(i in 1:nCampos){
  
  # get NA indexes
  m <-  which(is.na(RA_Sinonimos[,i]))
  
  if(length(m)==0){
    
    z <- c(RA_Sinonimos[,i])
    
  } else {
    # convert into a list
    z <- c(RA_Sinonimos[,i][1:min(m)-1,]) 
  }  
  # convert into chart
  z <- unlist(z) 
  
  myChar <- str_c(z,collapse = ";")  
  
  if(i==1){
    synonyms_RA <- c(myChar)
    
  } else {
    
    synonyms_RA <- c(synonyms_RA,myChar)  
    
  }
}

# to upper case. The synonims list ready to use
synonyms_RA <- toupper(synonyms_RA)

```



To see the relevance of the stopwords created, let's compare the frequency of the terms
without and with stopwords. 

```{r run analysis_AB }
# AB --run termExtraction()

# extract term with and whithout stopwords RA. ngrams = 1 to 2.


AB_Rawn1 <- termExtraction(myDF,Field="AB",ngrams = 1, remove.terms = sw)

AB_Rawn1 <- sort(table(unlist(strsplit(AB_Rawn1$AB_TM,split=";"))),decreasing = TRUE)

AB_Rawn1DF <- as.data.frame(AB_Rawn1)

AB_Rawn2 <- termExtraction(myDF,Field="AB",ngrams = 2, remove.terms = sw)

AB_Rawn2 <- sort(table(unlist(strsplit(AB_Rawn2$AB_TM,split=";"))),decreasing = TRUE)

AB_Rawn2DF <- as.data.frame(AB_Rawn2)



#merge al in one Df to be shown in a wordcloud graph
AB_Raw <- rbind(AB_Rawn1DF,AB_Rawn2DF)

# we extract the terms without grouping by synonyms. we then use it to know the repetitions of each term without grouping. ngram=1 to 2

RA_Keyword_AB_Rawn1 <- termExtraction(myDF,Field="AB",ngrams = 1, remove.terms = remove.terms)

AB_TermsRawn1 <- sort(table(unlist(strsplit(RA_Keyword_AB_Rawn1$AB_TM,split=";"))),decreasing = TRUE)

AB_TermsRawn1DF <- as.data.frame(AB_TermsRawn1)

RA_Keyword_AB_Rawn2 <- termExtraction(myDF,Field="AB",ngrams = 2, remove.terms = remove.terms)

AB_TermsRawn2 <- sort(table(unlist(strsplit(RA_Keyword_AB_Rawn2$AB_TM,split=";"))),decreasing = TRUE)

AB_TermsRawn2DF <- as.data.frame(AB_TermsRawn2)


#group all in 1 Data Frame
AB_terms.noSin <- rbind(AB_TermsRawn1DF,AB_TermsRawn2DF)

#export to csv, we will use it later with data4bubble and bubble vertices 
write.csv2(AB_terms.noSin,file="your path/AB_Terms_No_Sin.csv")


# Repeat the same work but using the RA_synonyms. we extract terms grouped by synonyms
RA_Keyword_AB_n1 <- termExtraction(myDF,Field="AB",ngrams = 1, remove.terms = remove.terms,synonyms = synonyms_RA)

AB_Terms_n1 <- sort(table(unlist(strsplit(RA_Keyword_AB_n1 $AB_TM,split=";"))),decreasing = TRUE)

AB_TermsDF_n1 <- as.data.frame(AB_Terms_n1)

RA_Keyword_AB_n2 <- termExtraction(myDF,Field="AB",ngrams = 2, remove.terms = remove.terms,synonyms = synonyms_RA)

AB_Terms_n2 <- sort(table(unlist(strsplit(RA_Keyword_AB_n2 $AB_TM,split=";"))),decreasing = TRUE)

AB_TermsDF_n2 <- as.data.frame(AB_Terms_n2)

AB_TermsDF <- rbind(AB_TermsDF_n1,AB_TermsDF_n2)

#export to csv
write.csv2(AB_TermsDF,file="your path/AB_Terms.csv")


```


### wordcloud graphs

We emphasize the relevance of doing the analysis with stopwords and synonyms. We focus on the keywords of the abstracts(AB)

```{r wordCloud plot}


#AB cloud

# we work with the top 200 words


# the top 200 words without synonyms nor RA stopwords
AB_Top_Term_raw <-  AB_Raw[1:200,] 

wordcloud2(AB_Top_Term_raw,size = 0.75, minSize = 0.1, gridSize =  0,
    fontFamily = 'Segoe UI', fontWeight = 'bold',
    color = 'random-light', backgroundColor = "white",
    minRotation = -pi/4, maxRotation = pi/4, shuffle = TRUE,
    rotateRatio = 0.4, shape = 'circle', ellipticity = 0.65,
    widgetsize = NULL, figPath = NULL, hoverFunction = NULL)

# without synonyms but with RA Stopwords 
AB_Top_Term_noSin <- AB_terms.noSin[1:200,]


wordcloud2(AB_Top_Term_noSin,size = 0.4, minSize = 0.1, gridSize =  0,
    fontFamily = 'Segoe UI', fontWeight = 'bold',
    color = 'random-light', backgroundColor = "white",
    minRotation = -pi/4, maxRotation = pi/4, shuffle = TRUE,
    rotateRatio = 0.4, shape = 'circle', ellipticity = 0.65,
    widgetsize = NULL, figPath = NULL, hoverFunction = NULL)



# With synonyms and RA stopwordswith more than 24 frequency.
AB_Top_Term <- AB_TermsDF[AB_TermsDF$Freq>24,]

wordcloud2(AB_Top_Term,size = 0.4, minSize = 0.2, gridSize =  0,
    fontFamily = 'Segoe UI', fontWeight = 'bold',
    color = 'random-dark', backgroundColor = "white",
    minRotation = -pi/4, maxRotation = pi/4, shuffle = TRUE,
    rotateRatio = 0.4, shape = 'circle', ellipticity = 0.65,
    widgetsize = NULL, figPath = NULL, hoverFunction = NULL)

```

## repreentation of the RA_synonym thesaurus.


```{r Synonyms description through a bubble graph}

# libraries
library(ggraph)
library(igraph)
library(broom)
library(tidyverse)


library(dplyr)
library(readxl)
library(viridis)
# Add the data.tree library
library(data.tree)
library(ggrepel)



# load data

# to complete this data I have used the output AB_Terms, which has already been filtered with stopwords and synonyms

my_Sinonimos <- read_excel("your path/RA_sinonimos.xlsx",sheet = "Data4Bubble")

my_vertices <- read_excel("your path/RA_sinonimos.xlsx",sheet = "BubbleVertices")

edges.1 <- my_Sinonimos[,1:2]
edges.1 <- as.data.frame(edges.1) #convierto a data frame

my_vertices <- as.data.frame(my_vertices)

# Transform it in a 'tree' format
tree <- FromDataFrameNetwork(edges.1)

# Then I can easily get the level of each node, and add it to the initial data frame:
mylevels.1 <- data.frame( name=tree$Get('name'), level=tree$Get("level") )
my_vertices <- my_vertices %>% 
  left_join(., mylevels.1, by=c("name"="name"))

# Now we can add label for level1 and 2 only for example:
my_vertices <- my_vertices %>% 
  mutate(new_label=ifelse(level==2, Shortname, NA))


# Now we can add label for level1 and 2 only for example:
my_vertices <- my_vertices %>% 
  mutate(new_label_2=ifelse(level==3, Shortname, NA))

# build the graph objet
 mygraph.1 <- graph_from_data_frame( edges.1, vertices=my_vertices )

pp <-  ggraph(mygraph.1, layout = 'circlepack', weight=size) + 
  geom_node_circle(aes(fill = as.factor(depth), color = as.factor(depth) )) +
    scale_fill_manual(values=c("0" = "white", "1" = "white", "2" =  mako(3)[2], "3"=mako(3)[3])) +
  scale_color_manual( values=c("0" =  "white", "1" = "lightblue", "2" = "black", "3"="black") ) +
  geom_node_label( aes(label=new_label_2), vjust="bottom",size=3.5, repel = TRUE) +
  theme_void() +
  theme(legend.position="TRUE", plot.margin = unit(rep(0,4), "cm"))


pp


```

## Relational analysis

### we define the relation between synonyms and clusters

```{r networkGraph synonims}
library(readxl)
library(ggraph)
library(igraph)


cluster.family.edges  <- read_excel("your path/RA_sinonimos.xlsx",sheet = "networkGraph")

cluster.family.vertices  <- read_excel("your path/RA_sinonimos.xlsx",sheet = "netGraphVer")

#defining the data frame containing the links
cluster.family.edges <- as.data.frame(cluster.family.edges)
cluster.family.vertices <- as.data.frame(cluster.family.vertices)


#------------------------------------------------------------------------------------------


# building the graph object
 mygraph.2 <- graph_from_data_frame( cluster.family.edges, vertices=cluster.family.vertices )

pp <- ggraph(mygraph.2, layout="stress")+
 geom_edge_link0(aes(edge_colour="lightblue")) +
  geom_node_point(aes(fill="clu",size=cluster.family.vertices$size),shape=21)+
  geom_node_label(aes(filter = textSize>=3 ,label=Shortname, size=textSize*8),repel = TRUE)+
  geom_node_text(aes(filter = textSize==2 ,label=Shortname, size=textSize*10, fontface="bold"),repel = TRUE)+
   scale_fill_brewer(palette = "Accent")+
  coord_fixed() +
  theme_void()+
  theme(legend.position = "FALSE")
pp

```


## cleanning no relevant abstracts

after reading the abstracts we realize that some of them are not relevant for the study, for example the paper is a biblimetric analysis so it is just a descriptive analysis of the research. The issues treated in those papers are not included in any cluster.

```{r abstracts cleanning}

# delete the references where no abstract is found
noAB_Rows<-which(is.na(w_sDF$AB))
w_sDF_ABClean<-w_sDF[-c(noAB_Rows),]

AB_clean <- cbind.data.frame(w_sDF_ABClean$PY,w_sDF_ABClean$TI,w_sDF_ABClean$AU,w_sDF_ABClean$AB)

write_xlsx(AB_clean,"your path/Abstract_clean.xlsx")
```


### Buuilding the author/subject heatmap:

----------------------------------------------------------------------------


```{r upload data and build data frame}
# import from excel

mapa_calor_AU <- read_excel("your path/mapa_calor_AU 210522.xlsx", sheet = "AU_Clust") 

#we count the number of fields you have in the df map_heat_AU to know how many Themes we have.
nCamposTemas <- ncol(mapa_calor_AU)


# I create the data frame for the ABs, columns 6-24 is where the topics are identified.
mapa_calor_AB <- cbind(Id_AB=mapa_calor_AU$id_AB,TI=mapa_calor_AU$TI,mapa_calor_AU[,6:24])

# remove the title of the DF to be plotted
myvars <- names(mapa_calor_AB) %in% c("TI")
data.AB <- mapa_calor_AB[!myvars] 

# replace NA by zero
data.AB[is.na(data.AB)] <- 0 



# 18 topics
data.AB<- data.AB[,2:20] 



# from the matrix containing all the data I obtain the subgroups of abstracts that have a 1 in one of the topics included in each cluster.
c.1 <- apply(data.AB[,1:4],1,sum)
c.2 <- apply(data.AB[,5:8],1,sum)
c.3 <- data.AB[,9]
c.4 <- apply(data.AB[,10:14],1,sum)
c.5 <- apply(data.AB[,15:19],1,sum)


# I create new extended Df for each cluster
data.AB.c.x <- cbind(data.AB,c.1,c.2,c.3,c.4,c.5)

# I create a new column with the sum of all the clusters to detect those ABs that have none
C.X <- apply(data.AB.c.x[,20:24],1,sum)

# add column to the complete data frame

data.AB.c.x <- cbind(data.AB.c.x,C.X)

# I eliminate those rows whose C.X is equal to zero because they are abstracts that are not included in any cluster.

# indexing
data.AB.Clean <- which(data.AB.c.x$C.X!=0)

# data selection
data.AB.c.x <- data.AB.c.x[c(data.AB.Clean),] # DF ready to work on it


```

## Heatmap graph

```{r df para mapa calor AB}

library(bipartite)


# change to matrix
data.AB.Clean <- as.matrix(data.AB.Clean)


par(cex.main=1, cex.lab=0.7, cex.axis=0.7)

heatmap.2(t(data.AB),
          margins = c(5,11),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","white","darkblue")),
          dendrogram = "col",
          density.info = "none",
          trace="both",
          tracecol = "lightblue",
        rowsep=c(4,8,9,14),
        sepcolor="red",
        
        lhei = c(1,7),lwid = c(0.5,4),
        xlab="Abstract",
        ylab="",

        key=FALSE,
      offsetRow = 0
         
        )


```

##individual heatmap by cluster


```{r heatmap by cluster}


# -------- cluster 1 -----------------------------------------
idx.c <- which(data.AB.c.x$c.1>0)
data.AB.c.1 <- data.AB.c.x[c(idx.c),]

# to matrix ready for heatmap.2

data.AB.c.1 <- as.matrix(data.AB.c.1[,1:19])

# HEATMAP C1


x_title <- paste(nrow(data.AB.c.1)," abstracts in C1")

  heatmap.2(t(data.AB.c.1[,1:19]),
          margins = c(5,11),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","white","darkblue")),
          dendrogram = "col",
          density.info = "none",
          trace="both",
          tracecol = "lightblue",
          linecol = "white",
        rowsep=c(4,8,9,14),
        sepcolor="red",
        lhei = c(1,7),lwid = c(0.5,4),
        xlab=x_title,
        ylab="Synonyms",
        key=FALSE,
      offsetRow = 0
          )

# -------- cluster 2 -----------------------------------------
idx.c <- which(data.AB.c.x$c.2>0)
data.AB.c.2 <- data.AB.c.x[c(idx.c),]



data.AB.c.2 <- as.matrix(data.AB.c.2[,1:19])


x_title <- paste(nrow(data.AB.c.2)," abstracts in C2")

  heatmap.2(t(data.AB.c.2),
          margins = c(5,11),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","white","darkblue")),
          dendrogram = "col",
          density.info = "none",
          trace="both",
          tracecol = "lightblue",
          linecol = "white",
        rowsep=c(4,8,9,14),
        sepcolor="red",
        lhei = c(1,7),lwid = c(0.5,4),
        xlab=x_title,
        ylab="Synonyms",
        key=FALSE,
      offsetRow = 0
          )
  
  # -------- cluster 3 -----------------------------------------
idx.c <- which(data.AB.c.x$c.3>0)
data.AB.c.3 <- data.AB.c.x[c(idx.c),]


data.AB.c.3 <- as.matrix(data.AB.c.3[,1:19])


x_title <- paste(nrow(data.AB.c.3)," abstracts in C3")

  heatmap.2(t(data.AB.c.3),
          margins = c(5,11),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","white","darkblue")),
          dendrogram = "col",
          density.info = "none",
          trace="both",
          tracecol = "lightblue",
          linecol = "white",
        rowsep=c(4,8,9,14),
        sepcolor="red",
        lhei = c(1,7),lwid = c(0.5,4),
        xlab=x_title,
        ylab="Synonyms",
        key=FALSE,
      offsetRow = 0
          )
  
 # -------- cluster 4 -----------------------------------------
idx.c <- which(data.AB.c.x$c.4>0)
data.AB.c.4 <- data.AB.c.x[c(idx.c),]


data.AB.c.4 <- as.matrix(data.AB.c.4[,1:19])


x_title <- paste(nrow(data.AB.c.4)," abstracts in C4")

  heatmap.2(t(data.AB.c.4),
          margins = c(5,11),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","white","darkblue")),
          dendrogram = "col",
          density.info = "none",
          trace="both",
          tracecol = "lightblue",
          linecol = "white",
        rowsep=c(4,8,9,14),
        sepcolor="red",
        lhei = c(1,7),lwid = c(0.5,4),
        xlab=x_title,
        ylab="Synonyms",
        key=FALSE,
      offsetRow = 0
          )  
  
 # -------- cluster 5 -----------------------------------------
idx.c <- which(data.AB.c.x$c.5>0)
data.AB.c.5 <- data.AB.c.x[c(idx.c),]


data.AB.c.5 <- as.matrix(data.AB.c.5[,1:19])


x_title <- paste(nrow(data.AB.c.5)," abstracts in C5")

  heatmap.2(t(data.AB.c.5),
          margins = c(5,11),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","white","darkblue")),
          dendrogram = "col",
          density.info = "none",
          trace="both",
          tracecol = "lightblue",
        rowsep=c(4,8,9,14),
        sepcolor="red",
        lhei = c(1,7),lwid = c(0.5,4),
        xlab=x_title,
        ylab="Synonyms",
        key=FALSE,
      offsetRow = 0
          )  
```

## Authors heatmap

```{r mapa calor autores- Datos}
# create single author list from the dataframe with abstracts and topics
listaAU <- str_split(as.character(mapa_calor_AU$AU), ";")

nAU <- lengths(listaAU) # number of authors per AB
myAU <- unlist(listaAU) # vector of authors
  
myAU <- unique(myAU) # single author vector

nUnqAU <- length(myAU) # number of unique authors



# we will assign to each author an index in which we will identify in which articles of the DF mapa_calor_AU appears.

nAB <- nrow(mapa_calor_AU) #  abstracts

#  AU/Topics matrix
AUThemMtx <- data.frame(mapa_calor_AU[,6:24])# lfirst 4 fields are not used

AUThemMtx[is.na(AUThemMtx)] <- 0 #we change NA to zero to be able to sum the columns


# I create a matrix of zeros to add up the partial results.
myTempMatrix <- data.frame(matrix(0,nUnqAU, ncol(AUThemMtx)))

colnames(myTempMatrix) <- colnames(AUThemMtx)

# start allocation loop

for(i in 1: nUnqAU){
  
   # I get the index where the authors are, with the grepl function I find the partial matching between the characters of the AU column.
  idx <-  which(grepl(myAU[i],mapa_calor_AU$AU))
  
  # I have to sum by column each row of idx
  
  a <- AUThemMtx[c(idx),] # I get the subset referring to the author
  aSum <- colSums(a)      # sum of all columns
  
  # I add the results to the author's row
  myTempMatrix[i,] <- myTempMatrix[i,]+aSum 
  
}

# data frame with unique authors and the topics they have dealt with
AU_Tema <- data.frame(myAU,myTempMatrix)

#I order the topics by the defined clusters, in each topic name I have added, at the beginning, its cluster number from 1 to 5, so when I order them I group them by cluster.

AU_Tema_ord <-AU_Tema[,2:20] # keep topic columns

AU_Tema_ord <- AU_Tema_ord[,order(colnames(AU_Tema_ord))] # las ordeno por nombre del tema

AU_Tema_ord <- data.frame(myAU,AU_Tema_ord)

AUThemMtx_ord <- AUThemMtx[,order(colnames(AUThemMtx))]

```

We generate the graphs for author analysis

```{r AU graph}


data <- AU_Tema 

dataOrd <- AU_Tema_ord

rownames(data) <- data[,1] # unique authors as row names
rownames(dataOrd) <- dataOrd[,1]


data <- data[,2:20] 
dataOrd <- dataOrd[,2:20]


colnames(data) <- colnames(AUThemMtx)
colnames(dataOrd) <- colnames(AUThemMtx_ord)

data.m <- as.matrix(data)
dataOrd.m<- as.matrix(dataOrd)



# We added 5 columns representing each cluster to do the analysis by cluster instead of cluster and family.

dataOrd$C1 <- rowSums(dataOrd[,1:4])
dataOrd$C2 <- rowSums(dataOrd[,5:8])
dataOrd$C3 <- dataOrd[,9]
dataOrd$C4 <- rowSums(dataOrd[,10:15])
dataOrd$C5 <- rowSums(dataOrd[,16:19])


au_clust <- dataOrd[,20:24]
au_clust.m <- as.matrix(au_clust)

# we plot the relationship between authors and clusters
library(igraph)



# network chart between authors and clusters
net <- graph_from_incidence_matrix(au_clust.m)

V(net)$color <- ifelse(V(net)$type, "lightblue", "salmon")
V(net)$shape <- ifelse(V(net)$type, "circle", "none")
V(net)$label.cex <- ifelse(V(net)$type, 1, 0.5)
E(net)$color <- "gray"
E(net)$color <- ifelse(E(net)$color==top20AU$Author,"red")

plot(net, vertex.size=10, vertex.label.color="black", 
     edge.lty=2, edge.color="gray", 
     main="Author relations with Cluster")


# heatmap with families/clusters and authors

par(cex.main=1, cex.lab=0.7,cex.axis=2)

heatmap.2(t(dataOrd.m),
          margins = c(5,11),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","blue","darkblue")),
          dendrogram = "none",
          density.info = "none",
        trace="none",
        rowsep=c(4,9,10,15),
        sepcolor="red",
        lhei = c(5,15),lwid = c(3,15),
        xlab="Author",
        ylab="Theme",
        main="heatmap AU/Theme"
      )


```

### heatmap top 20 autores

as we have so many authors, the graph does not show very well the
concentration of authors/topics. Let's redo the heatmap but only for the top 20 AU.
I need to get the top 20 authors from the bibliometrix results.


```{r 20TopAU heatmap}

library(bipartite)

# I import the top 20 authors, I could generate them with the Hindex function of the bibliometrix package, but for now I import them from excel (I got them with biblioshiny).

top20AU <- read_excel("yout path/top20AU.xlsx")

myTop20AU_Tema <- AU_Tema_ord[AU_Tema_ord$myAU %in% top20AU$Author,]


data20 <- myTop20AU_Tema

rownames(data20) <- data20[,1] 


data20 <- data20[,2:20]

colnames(data20) <- colnames(AUThemMtx_ord)



data20$C1 <- rowSums(data20[,1:4])
data20$C2 <- rowSums(data20[,5:8])
data20$C3 <- data20[,9]
data20$C4 <- rowSums(data20[,10:14])
data20$C5 <- rowSums(data20[,15:19])

au20_clust <- data20[,20:24]
au20_clust.m <- as.matrix(au20_clust)




# we plot the relationship between authors and clusters

plotweb(au20_clust.m, labsize = 1, arrow = "no", col.interaction = "lightblue", 
        col.high = "tomato", col.low = "grey80" )

# calculating the modules
mod20 <- computeModules(au20_clust.m)
pp <- plotModuleWeb(mod20)


par(cex.main=1, cex.lab=0.7,cex.axis=2)


heatmap.2(t(au20_clust.m),
          margins = c(10,5),
          Colv = TRUE, Rowv = FALSE, # remove dendrogram
          col = colorRampPalette(c("white","blue","darkblue")),
          dendrogram = "col",
          density.info = "none",
          trace="both",
        rowsep=c(4,9,10,15),
        sepcolor="red",
        lhei = c(5,15),lwid = c(3,15),
        xlab="",
        ylab="",
        main="heatmap 20 AU/Theme"
        )

```
